### 2016-01-16 p01-ch02-2013/paper.tex
Fix long captions in figures and tables
Change bib style to 'american' from the original template

\begin{figure}[t]
\begin{align}
C &::= \textbf{\jtt{class}} \; \mathsf{N} \; \textbf{\jtt{begin}} \; V^? \; \{M\}^* \; \textbf{\jtt{end}} \\
M_{sig} &::=
%\textbf{\jtt{op}} \; 
\mathsf{N}(\overline{T \: x}) \\ 
M &::= \{ M_{sig} == \{V \; ;\}^? S \} \\
V &::= \textbf{\jtt{var}} \; \{\{x\},^+ \; : \; \mathsf{T} \; \{ = e\}^? \},^+ \\
S &::=  x := e\; | \\
 &::= x := \textbf{\jtt{new}} \; \mathsf{T}(e^?) \; |\\
&:= f = e \; ! \; m(\overline{e}) \; \textbf{\jtt{deadline}}(e) \: | \\
 &::= x := f.\gett(e^?) \; | \\
  &::= \textbf{\jtt{return}} \; e  \; | \\
  &::= S \; ; \; S \; | \\
  &::= \textbf{\jtt{if}} \; (b) \; \textbf{\jtt{then}} \; S \; \textbf{\jtt{else}} \; S \; \textbf{\jtt{end}}  \; | \\
  &::= \textbf{\jtt{while}} \; (b) \; \{ \; S \; \} \; | \\
  &::= \textbf{\jtt{try}} \: \{ S \} \: \jtt{\textbf{catch}}(\mathsf{T}_{\jtt{Exception}} \; x) \: \{ \: S \: \}  
%E &::= B \; | \; V \\
%B &::= \textbf{\jtt{true}} \; | \; \textbf{\jtt{false}} \; | \; B \wedge B \; | \; B \vee B \; | \; %\textbf{\jtt{not}} \; B
\end{align}
\caption{
A kernel version of the real-time programming language.
The bold scripted \textbf{\jtt{keywords}} denote the reserved words in the language.
The over-lined $\overline{v}$ denotes a sequence  of syntactic entities $v$.
Both local and instance variables are denoted by $x$.
We assume distinguished local variables  $\jtt{this}$, $\jtt{myfuture}$, and  $\jtt{deadline}$ which
denote the actor itself, the  unique future corresponding to the process, and  its deadline,  respectively.
A distinguished instance variable $\jtt{time}$  denotes  the current time.
Any subscripted type $\mathsf{T}_{specialized}$ denotes a \textit{specialized} type of general type $\mathsf{T}$; 
e.g. $\mathsf{T}_{\jtt{Exception}}$ denotes all ``exception'' types.
A variable $f$ is in $\mathsf{T}_{future}$. 
\textsf{N} is a name (identifier) used for classes and method names.
%$e$ is in \textsf{Expression} ($E$);
$C$ denotes a class definition which consists of  a definition of its instance variables
and its methods;
$M_{sig}$ is a method signature; $M$ is a method definition; $S$ denotes a statement.
We abstract from the syntax the side-effect free expressions $e$ and
boolean expressions $b$.
%
%For simplicity, we drop the notation syntax to specify how $V$ can expand to different values along with arithmetic operations.
%\emph{Note} that small letters (e.g. $e$) are of type of their capital constructs (e.g. $E$).
}
\label{fig:grammar}
\end{figure}

@@

\begin{figure}[h]
% \begin{wrapfigure}{r}{0.4\textwidth}
% \vspace{-40pt}
\begin{center}
\includegraphics[scale=0.4]{figs/DM}
\end{center}
% \vspace{-20pt}
\caption{Fredhopper's Controller life cycle for remote data processing}
\label{fig:frh-dm}
% \vspace{-10pt}
% \end{wrapfigure}
\end{figure}

>>>>

\begin{figure}[t]
\begin{align}
C &::= \textbf{\jtt{class}} \; \mathsf{N} \; \textbf{\jtt{begin}} \; V^? \; \{M\}^* \; \textbf{\jtt{end}} \\
M_{sig} &::=
%\textbf{\jtt{op}} \; 
\mathsf{N}(\overline{T \: x}) \\ 
M &::= \{ M_{sig} == \{V \; ;\}^? S \} \\
V &::= \textbf{\jtt{var}} \; \{\{x\},^+ \; : \; \mathsf{T} \; \{ = e\}^? \},^+ \\
S &::=  x := e\; | \\
 &::= x := \textbf{\jtt{new}} \; \mathsf{T}(e^?) \; |\\
&:= f = e \; ! \; m(\overline{e}) \; \textbf{\jtt{deadline}}(e) \: | \\
 &::= x := f.\gett(e^?) \; | \\
  &::= \textbf{\jtt{return}} \; e  \; | \\
  &::= S \; ; \; S \; | \\
  &::= \textbf{\jtt{if}} \; (b) \; \textbf{\jtt{then}} \; S \; \textbf{\jtt{else}} \; S \; \textbf{\jtt{end}}  \; | \\
  &::= \textbf{\jtt{while}} \; (b) \; \{ \; S \; \} \; | \\
  &::= \textbf{\jtt{try}} \: \{ S \} \: \jtt{\textbf{catch}}(\mathsf{T}_{\jtt{Exception}} \; x) \: \{ \: S \: \}  
%E &::= B \; | \; V \\
%B &::= \textbf{\jtt{true}} \; | \; \textbf{\jtt{false}} \; | \; B \wedge B \; | \; B \vee B \; | \; %\textbf{\jtt{not}} \; B
\end{align}
\caption[A kernel version of the real-time programming language]{
A kernel version of the real-time programming language.
The bold scripted \textbf{\jtt{keywords}} denote the reserved words in the language.
The over-lined $\overline{v}$ denotes a sequence  of syntactic entities $v$.
Both local and instance variables are denoted by $x$.
We assume distinguished local variables  $\jtt{this}$, $\jtt{myfuture}$, and  $\jtt{deadline}$ which
denote the actor itself, the  unique future corresponding to the process, and  its deadline,  respectively.
A distinguished instance variable $\jtt{time}$  denotes  the current time.
Any subscripted type $\mathsf{T}_{specialized}$ denotes a \textit{specialized} type of general type $\mathsf{T}$; 
e.g. $\mathsf{T}_{\jtt{Exception}}$ denotes all ``exception'' types.
A variable $f$ is in $\mathsf{T}_{future}$. 
\textsf{N} is a name (identifier) used for classes and method names.
%$e$ is in \textsf{Expression} ($E$);
$C$ denotes a class definition which consists of  a definition of its instance variables
and its methods;
$M_{sig}$ is a method signature; $M$ is a method definition; $S$ denotes a statement.
We abstract from the syntax the side-effect free expressions $e$ and
boolean expressions $b$.
%
%For simplicity, we drop the notation syntax to specify how $V$ can expand to different values along with arithmetic operations.
%\emph{Note} that small letters (e.g. $e$) are of type of their capital constructs (e.g. $E$).
}
\label{fig:grammar}
\end{figure}

@@

\begin{figure}[h]
% \begin{wrapfigure}{r}{0.4\textwidth}
% \vspace{-40pt}
\begin{center}
\includegraphics[scale=0.4]{figs/DM}
\end{center}
% \vspace{-20pt}
\caption[Life cycle for remote data processing]{Fredhopper's Controller life cycle for remote data processing}
\label{fig:frh-dm}
% \vspace{-10pt}
% \end{wrapfigure}
\end{figure}
